Missing data: Current practice in football research and recommendations for reporting missingness

### 2020-09-01 paper/paper.Rmd
title change

---
title: "Missing data in sports science: Current practice in football research and recommendations for reporting missingness"
authors: David N Borg(1), Robert Nguyen(2), Nicholas J Tierney(3,4)
output: 
  html_document:
    toc: true
    toc_float: true
    keep_md: true
bibliography: references.bib
---

>>>>

---
title: "Missing data: Current practice in football research and recommendations for reporting missingness"
authors: David N Borg(1), Robert Nguyen(2), Nicholas J Tierney(3,4)
output: 
  html_document:
    toc: true
    toc_float: true
    keep_md: true
bibliography: references.bib
---
